Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery.

### 2024-03-01 docs/_tex/index.tex
Pierre comments

\subsection{Green Macrophytes
Discrimination}\label{green-macrophytes-discrimination}

@@

The discrimination of seagrasses from green macroalgae presents
significant challenges, primarily due to the shared pigment composition
between these taxa, as depicted in Figure~\ref{fig-Pigm} but also by the
frequent spatial mixing of these green macrophytes. This similarity in
pigment composition, including photosynthetic and carotenoid pigments
like chlorophyll b and c, fucoxanthin, and neoxanthin, results in
spectral signatures that are often indistinguishable to non expererences
This spectral overlap is further complicated by the intermingling of
seagrasses and green macroalgae in the same spatial locations, posing a
significant challenge for remote sensing aimed at accurately mapping and
monitoring coastal ecosystems. Our study addresses these complexities by
utilizing high-resolution drone imagery with 10 spectral bands.
\citep{Davies2023} has shown that having at least 8 spectral bands
ranging between 500 nm to 850 nm with on band at 530 nm and another one
at 730 nm is crucial to accurately discriminate green macrophytes.

@@

The Micasense RedEdge-MX DUAL camera used in this study meets these two
criteria, enabling the classifier to achieve 97\% of accuracy between
these two classes (Figure~\ref{fig-ValidationGreen}). Even if the
pigment compostion of green macrophytes is similar, differences in the
spectral shape can still be observed (Figure~\ref{fig-vegetation}).
Several factors can explain these differences such has different pigment
concentration en proportion, different cellular organisation and 3D
disposition of the plant a whole on the intertidal mudflat
\citep[\citep{kirk1994light},
\citep{hedley2018influence}]{beach1997vivo}.

The VIP analysis of the Neural Network model (see Fig. VIP) shows that
the 531 nm band is the most important spectral band for accurately
identifying Chlorophyceae. In fact, at this wavelength, Chlorophyceae
exhibits the highest reflectance among all other classes, highlighting
the difference in accessories carotenoid proportion between seagrasses
and green algae (\citep{repolho2017seagrass}).

Concerning Phaeophyceae, the thick cell walls of plant of this class
make it really reflective in the infrared part of the spectra whereas
the presence of Fucoxanthin and Zeaxanthin result in a low reflectance
in the visible part of the electomagnetic spectra. These two key
features has been identified by the Neural Network as the two principale
predictors to accuratly identify Brown algae (Figure~\ref{fig-VIP}, )

\subsection{Spectral and Temporal Resolution impact on the
prediction}\label{spectral-and-temporal-resolution-impact-on-the-prediction}

>>>>

\subsection{Vegetation Discrimination}\label{vegetation-discrimination}

@@

The discrimination of seagrasses from green macroalgae presents
significant challenges, primarily due to the shared pigment composition
between these taxa, as depicted in Figure~\ref{fig-Pigm} but also by the
frequent spatial mixing of these green macrophytes. This similarity in
pigment composition, including photosynthetic and carotenoid pigments
like chlorophyll b and c, fucoxanthin, and neoxanthin, results in
spectral signatures that are often indistinguishable to non exper eyes.
This spectral overlap is further complicated by the intermingling of
seagrasses and green macroalgae in the same spatial locations, posing a
significant challenge for remote sensing aimed at accurately mapping and
monitoring coastal ecosystems. Our study addresses these complexities by
utilizing high-resolution drone imagery with 10 spectral bands.
\citep{Davies2023} has shown that having at least 8 spectral bands
ranging between 500 nm to 850 nm with including a band at 530 nm and
another one at 730 nm is crucial to accurately discriminate green
macrophytes.

@@

The Micasense RedEdge-MX DUAL camera used in this study meets these two
criteria, enabling the classifier to achieve 97\% of accuracy between
these two classes (Figure~\ref{fig-ValidationGreen}). Even if the
pigment compostion of green macrophytes is similar, differences in the
spectral shape can still be observed (Figure~\ref{fig-vegetation}).
Several factors can explain these differences such has different pigment
concentration or proportion, different cellular organisation and 3D
disposition of the plant a whole on the intertidal mudflat
\citep[\citep{kirk1994light},
\citep{hedley2018influence}]{beach1997vivo}.

The VIP analysis of the Neural Network model (Figure~\ref{fig-VIP})
shows that the 531 nm band is the most important spectral band for
accurately identifying Chlorophyceae. In fact, at this wavelength,
Chlorophyceae exhibits the highest reflectance among all other classes,
highlighting the difference in accessories carotenoid proportion between
seagrasses and green algae (\citep{repolho2017seagrass}).

Concerning Phaeophyceae, the thick cell walls of plant of this class
make it really reflective in the infrared part of the spectra whereas
the presence of Fucoxanthin and Zeaxanthin result in a low reflectance
in the visible part of the electromagnetic spectra. These two key
features has been identified by the Neural Network as the two principal
predictors to accurately identify Brown algae (Figure~\ref{fig-VIP}).
Similarly, the presence of phycoerythrin and phycocyanin in Rhodophyceae
contributes to the lowest reflectance among all classes in the spectral
range of 560 to 615 nm (Figure~\ref{fig-VIP}). The band at 560 nm has
been identified as important for accurately identifying this class
Resolution impact on the prediction. Regarding Bacillariophyceae, the
VIP analysis (Figure~\ref{fig-VIP}) indicates that 475 nm is the most
important predictor for this class. This could be attributed to the
absence of lutein, neoxanthin, and zeaxanthin in diatoms, absorbing in
the blue part of spectra, resulting in the highest visible reflectance
among all classes. Furethemore, it is vegetation with the lowest
concentration of chlorphyll-a, pigment absorbing light both in the blue
and the red. The transparency of Bacillariophyceae makes the reflectance
of the sediment part of the overall reflectance of Bacillariophyceae,
further explaining the high reflectance in the blue.

\subsection{\texorpdfstring{\textbf{Spectral Spatial Temporal Resolution
impact on the
prediction}}{Spectral Spatial Temporal Resolution impact on the prediction}}\label{spectral-spatial-temporal-resolution-impact-on-the-prediction}

### 2024-03-01 index.qmd
Pierre comments

## Green Macrophytes Discrimination

@@

The discrimination of seagrasses from green macroalgae presents significant challenges, primarily due to the shared pigment composition between these taxa, as depicted in @fig-Pigm but also by the frequent spatial mixing of these green macrophytes. This similarity in pigment composition, including photosynthetic and carotenoid pigments like chlorophyll b and c, fucoxanthin, and neoxanthin, results in spectral signatures that are often indistinguishable to non expererences This spectral overlap is further complicated by the intermingling of seagrasses and green macroalgae in the same spatial locations, posing a significant challenge for remote sensing aimed at accurately mapping and monitoring coastal ecosystems. Our study addresses these complexities by utilizing high-resolution drone imagery with 10 spectral bands. @Davies2023 has shown that having at least 8 spectral bands ranging between 500 nm to 850 nm with on band at 530 nm and another one at 730 nm is crucial to accurately discriminate green macrophytes.

@@

::: column
The Micasense RedEdge-MX DUAL camera used in this study meets these two criteria, enabling the classifier to achieve `r round(validation_metrics_green$overall[[1]],2)*100`% of accuracy between these two classes (@fig-ValidationGreen). Even if the pigment compostion of green macrophytes is similar, differences in the spectral shape can still be observed (@fig-vegetation). Several factors can explain these differences such has different pigment concentration en proportion, different cellular organisation and 3D disposition of the plant a whole on the intertidal mudflat [@beach1997vivo, @kirk1994light, @hedley2018influence].
:::
:::

The VIP analysis of the Neural Network model (see Fig. VIP) shows that the 531 nm band is the most important spectral band for accurately identifying Chlorophyceae. In fact, at this wavelength, Chlorophyceae exhibits the highest reflectance among all other classes, highlighting the difference in accessories carotenoid proportion between seagrasses and green algae (@repolho2017seagrass).

Concerning Phaeophyceae, the thick cell walls of plant of this class make it really reflective in the infrared part of the spectra whereas the presence of Fucoxanthin and Zeaxanthin result in a low reflectance in the visible part of the electomagnetic spectra. These two key features has been identified by the Neural Network as the two principale predictors to accuratly identify Brown algae (@fig-VIP, )

## Spectral and Temporal Resolution impact on the prediction

>>>>

## Vegetation Discrimination

@@

The discrimination of seagrasses from green macroalgae presents significant challenges, primarily due to the shared pigment composition between these taxa, as depicted in @fig-Pigm but also by the frequent spatial mixing of these green macrophytes. This similarity in pigment composition, including photosynthetic and carotenoid pigments like chlorophyll b and c, fucoxanthin, and neoxanthin, results in spectral signatures that are often indistinguishable to non exper eyes. This spectral overlap is further complicated by the intermingling of seagrasses and green macroalgae in the same spatial locations, posing a significant challenge for remote sensing aimed at accurately mapping and monitoring coastal ecosystems. Our study addresses these complexities by utilizing high-resolution drone imagery with 10 spectral bands. @Davies2023 has shown that having at least 8 spectral bands ranging between 500 nm to 850 nm with including a band at 530 nm and another one at 730 nm is crucial to accurately discriminate green macrophytes.

@@

::: column
The Micasense RedEdge-MX DUAL camera used in this study meets these two criteria, enabling the classifier to achieve `r round(validation_metrics_green$overall[[1]],2)*100`% of accuracy between these two classes (@fig-ValidationGreen). Even if the pigment compostion of green macrophytes is similar, differences in the spectral shape can still be observed (@fig-vegetation). Several factors can explain these differences such has different pigment concentration or proportion, different cellular organisation and 3D disposition of the plant a whole on the intertidal mudflat [@beach1997vivo, @kirk1994light, @hedley2018influence].
:::
:::

The VIP analysis of the Neural Network model (@fig-VIP) shows that the 531 nm band is the most important spectral band for accurately identifying Chlorophyceae. In fact, at this wavelength, Chlorophyceae exhibits the highest reflectance among all other classes, highlighting the difference in accessories carotenoid proportion between seagrasses and green algae (@repolho2017seagrass).

Concerning Phaeophyceae, the thick cell walls of plant of this class make it really reflective in the infrared part of the spectra whereas the presence of Fucoxanthin and Zeaxanthin result in a low reflectance in the visible part of the electromagnetic spectra. These two key features has been identified by the Neural Network as the two principal predictors to accurately identify Brown algae (@fig-VIP). Similarly, the presence of phycoerythrin and phycocyanin in Rhodophyceae contributes to the lowest reflectance among all classes in the spectral range of 560 to 615 nm (@fig-VIP). The band at 560 nm has been identified as important for accurately identifying this class Resolution impact on the prediction. Regarding Bacillariophyceae, the VIP analysis (@fig-VIP) indicates that 475 nm is the most important predictor for this class. This could be attributed to the absence of lutein, neoxanthin, and zeaxanthin in diatoms, absorbing in the blue part of spectra, resulting in the highest visible reflectance among all classes. Furethemore, it is vegetation with the lowest concentration of chlorphyll-a, pigment absorbing light both in the blue and the red. The transparency of Bacillariophyceae makes the reflectance of the sediment part of the overall reflectance of Bacillariophyceae, further explaining the high reflectance in the blue.

## **Spectral Spatial Temporal Resolution impact on the prediction**
